---
title: "EDAHomework1"
author: "Luke Gauthier"
format: html
editor: visual
---

# EDA Homework 1

#### Complete the following questions:

-   What is a barplot? Draw barplot for the 'drv' variable using R or Python.
-   What is a histogram? Draw histograms for highway miles per gallon. One for each drv type using R/Python. The histograms should be on the same scale for visual comparison.
-   What is a box plot? Draw box plots for highway miles per gallon variable - one for each drv type in R/Python. The box plots should be on the same scale for visual comparison. What can you conclude from this box plot?

##### Load Packages

```{r, message = FALSE}
library(tidyverse)
library(knitr)
library(DT)
library(dplyr)
```

##### Load Data

```{r}
dat_mpg <- mpg
dim(dat_mpg)
dat_mpg %>% head() %>% knitr::kable()
```

## What is a barplot? Draw a barplot for the 'drv' variable using R or Python.

a)  A barplot is a graph which shows a relationship between a value and a category.

```{r}
ggplot() + geom_bar(data = dat_mpg,
                    mapping = aes(x = drv), width = .3) +
  theme(legend.position = "none",
        text = element_text(size = 20),
        axis.text.x = element_text(angle = 0))
```

## What is a histogram? Draw histograms for highway miles per gallon. One for each drv type using R/Python. The histograms should be on the same scale for visual comparison.

a)  A Histogram is a graph which shows the frequency across a category.
b)  Drive type Forward is light blue, drive type 4 is light green, and drive type rear is pink

```{r}
drvF <- dplyr::filter(dat_mpg, drv %in% c('f'))
drv4 <- dplyr::filter(dat_mpg, drv %in% c('4'))
drvR <- dplyr::filter(dat_mpg, drv %in% c('r'))

drvFhist <- hist(drvF$hwy, main = "Front wheel drive Highway MPG")
drv4hist <- hist(drv4$hwy, main = "All wheel drive Highway MPG")
drvRhist <- hist(drvR$hwy, main = "Rear wheel drive Highway MPG")

plot(drvFhist, col = "lightblue", xlim = c(12, 45), ylim = c(0,64), main = "All Drive Types MPG")
plot(drv4hist, col = "lightgreen", add = TRUE)
plot(drvRhist, add = TRUE, col = "pink")
```

## What is a box plot? Draw box plots for highway miles per gallon variable - one for each drv type in R/Python. The box plots should be on the same scale for visual comparison. What can you conclude from this box plot?

a)  A box plot is is a graph to show the spread and skew of groups of data.

```{r}
boxDrvF <- drvF$hwy
boxDrv4 <- drv4$hwy
boxDrvR <- drvR$hwy

boxplot(boxDrvF, boxDrv4, boxDrvR, main = "Boxplots for each drv type", 
        names = c("Drv F", "Drv 4", "Drv R"), col = c("orange", "red", "blue"), 
        horizontal = TRUE)

```

b)  What can be concluded from this box plot is that rear wheel drive has the largest interquartile range. Four wheel drive has the lowest hwy mpg median but the largest range from min to max. Finally Front wheel drive has the highest mpg.
