---
title: "HW4"
author: "Luke Gauthier"
format: html
editor: visual
---

## HW4

- Repeat the simulation for A=1 and A=1.5. Show all three ROCs on the same plot with clear legends and labels. Keep all other parameters fixed: (MU_w = 0, SIGMA_w^2=1, k=10)
- Repeat the simulation for k=15, k=20, k=30. Show all three ROCs on the same plot with clear legends and labels. Keep all other parameters fixed: (MU_w=0, SIGMA_w^2=1, A=0.5)

## Simulation 1

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

### Adding libraries
```{r}
library(tidyverse)
library(ggplot2)
library(patchwork)
```

```{r}
# Number of MonteCarlo Trials
repM <- 10000

#Signal Model
A = 0.5
A2 = 1
A3 = 1.5
k <- 10
s <- rep(A, k)
s2 <- rep(A2, k)
s3 <- rep(A3, k)

#Noise Model
mu_w <- 0
var_w <- 1
sd_w <- sqrt(var_w)



#signal + noise
test_statistic_h0 = NA
for(iM in 1:repM){
  w <- rnorm(k, mean = mu_w, sd = sd_w)
  test_statistic_h0[iM] <- mean(w)
}

test_statistic_h1 = NA
for(iM in 1:repM){
  x <- A + rnorm(k, mean = mu_w, sd = sd_w)
  test_statistic_h1[iM] <- mean(x)
}

test_statistic_h2 = NA
for(iM in 1:repM){
  x2 <- A2 + rnorm(k, mean = mu_w, sd = sd_w)
  test_statistic_h2[iM] <- mean(x2)
}

test_statistic_h3 = NA
for(iM in 1:repM){
  x3 <- A3 + rnorm(k, mean = mu_w, sd = sd_w)
  test_statistic_h3[iM] <- mean(x3)
}

dat_sim <- 
  data.frame('test_statistic' = test_statistic_h0, 'label' = 'H0') %>%
  bind_rows(data.frame('test_statistic' = test_statistic_h1, 'label' = 'H1')) %>%
  bind_rows(data.frame('test_statistic' = test_statistic_h2, 'label' = 'H2')) %>%
  bind_rows(data.frame('test_statistic' = test_statistic_h3, 'label' = 'H3'))
```
### Plotting simulation 1
```{r}
ggplot(data = dat_sim, aes(x=test_statistic, fill = label)) + geom_density(alpha = 0.4)

th <- A/2

```
## Simulation 2
```{r}
# number of MonteCarlo trials
repM <- 10000

# Signal model
A = 0.5
k = 10
k2 <- 15
k3 <- 20
k4 <- 30
s <- rep(A, k)
s2 <- rep(A,k2)
s3 <- rep(A, k3)
s4 <- rep(A, k4)

test_statistic_k0 = NA
for(iM in 1:repM){
  w <- rnorm(k, mean = mu_w, sd = sd_w)
  test_statistic_k0[iM] <- mean(w)
}

test_statistic_k1 = NA
for(iM in 1:repM){
  x <- A + rnorm(k2, mean = mu_w, sd = sd_w)
  test_statistic_k1[iM] <- mean(x)
}

test_statistic_k2 = NA
for(iM in 1:repM){
  x2 <- A + rnorm(k3, mean = mu_w, sd = sd_w)
  test_statistic_k2[iM] <- mean(x2)
}

test_statistic_k3 = NA
for(iM in 1:repM){
  x3 <- A + rnorm(k4, mean = mu_w, sd = sd_w)
  test_statistic_k3[iM] <- mean(x3)
}

dat_sim2 <-
  data.frame('test_statistic' = test_statistic_k1, 'label' = 'K1') %>%
  bind_rows(data.frame('test_statistic' = test_statistic_k2, 'label' = 'K2')) %>%
  bind_rows(data.frame('test_statistic' = test_statistic_k3, 'label' = 'K3')) %>%
  mutate(
    A=A
  )
```

### Plotting Simulation 2
```{r}
ggplot(data = dat_sim2, aes(x=test_statistic, fill = label)) + geom_density(alpha = 0.5)
```
