---
title: "QuartoFlightsDataAnalysis"
author: "Luke Gauthier"
format: html
editor: visual
---

# Flights Data Analysis

## Questions

-   Had an arrival delay of two or more hours
-   Flew to Houston (IAH or HOU)
-   Were operated by United, American, or Delta
-   Departed in summer (July, August, and September)
-   arrived more than two hours late, but didn't leave late
-   were delayed by at least an hour, but made up over 30 minutes in flight
-   Departed between midnight and 6 am(inclusive)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Packages

```{r, message = FALSE}
library(tidyverse)
library(nycflights13)
library(knitr)
```

## Read and view data

```{r}
dat_flights <- read_csv("dat_flights.csv")
dim(dat_flights)

dat_flights %>% head() %>% knitr::kable()
```

## Filtering the data

#### Question 1:

What flights had a delay of greater than 2 hours?

```{r dat_flights}
filter(dat_flights, arr_delay >= 120)
```

#### Question 2:

What flights had a destination of Houston, Texas?

```{r dat_flights}
filter(dat_flights, dest== "IAH" | dest == "HOU")
```

#### Question 3:

Which flights were done by the the carriers United Airlines, American Airlines, and Delta?

```{r dat_flights}
filter(dat_flights, carrier == "UA" | carrier == "AA" | carrier == "DL")
```

#### Quesion 4:

Which flights took place during the summer (July, August, and September)?

```{r dat_flights}
filter(dat_flights, month == "7" | month == "8" | month == "9")
```

#### Question 5:

Which flights arrived more than 2 hours late but didn't leave late?

```{r dat_flights}
filter(dat_flights, arr_delay >= 120 & dep_delay == 0)
```

#### Question 6:

Which flights were delayed by at least one hour, but made up over 30 minutes in flight? \##### Part 1: Find the air scheduled air time

```{r dat_flights}
QuestionSix <- dat_flights %>%
  add_column(sched_air_time = abs(dat_flights$sched_dep_time - dat_flights$sched_arr_time))
QuestionSix
QuestionSix <- QuestionSix %>%
    add_column(air_time_diff = (QuestionSix$air_time - QuestionSix$sched_air_time))
QuestionSix
```

##### Part 2:

Filter the data to find the answer

```{r QuestionSix}
filter(QuestionSix, dep_delay >= 60 & air_time_diff <= -30)
```

#### Question 7:

Which flights departed between midnight and 6am (inclusive)?

```{r dat_flights}
filter(dat_flights, dep_time >= 0 & dep_time <= 600)
```
