---
title: "ClassNotes"
author: "Luke Gauthier"
format: html
editor: visual
---

# Class Notes 9/19/2023

Write code to plot uniform probability density function where a = 1 and b = 6

## Load libraries

```{r, message=FALSE}
library(tidyverse)
library(knitr)
library(DT)
```

### Probability Density Function Plot

```{r}
x <- seq(0,8, length = 100)
y <- dunif(x, min = 1, max = 6)
plot(x,y,type="l")
```

### Cumulative Distribution Function Plot

```{r}
a = 1
b = 6
x <- seq(0,7)
cdf <- punif(x, min = a, max = b)
plot(cdf, type="l")
```

### Generate 100 Random numbers based on PDF & Histogram plot

```{r}
a = 1
b = 6
rand <- runif(10000, min = a, max = b)
print(rand)
hist(rand, xlim = c(0,7))

```
### Normal Distribution
```{r}
x <- seq(-1,1, length = 100)
y <- dnorm(x, mean = 0, sd = 1)
plot(x,y, type = "l", main = "Normal Distribution", col = "blue")
rand2 <- rnorm(100)
hist(rand2)
```
### Problem
- Cyber security system to detect anomalies
- Response times of network requests are normally distributed with mean 100 m secs and a standard deviation of 20 m secs
- What is the probability that a network request takes between 80 m sec and 100 m sec to be processed?
#### Distribution of Network Requests
```{r}
x <- seq(0, 200)
y <- dnorm(x, mean = 100, sd = 20)
plot(x,y, type = "l", main = "Normal Dist. of Network Requests")
```
#### Probability that a network request takes between 80 msec and 100 msec to be processed
```{r} 
mu = 100
sigma = 20
probability = pnorm(100, mu, sigma) - pnorm(80, mu, sigma)
print(probability)
```